---
title: "Mark Druffel"
author: Mark Druffel
date: "`r Sys.Date()`"
output:
  pagedown::html_resume:
    #resume is the default from pagedown, keep it there or have to build all css structures
    css: ["resume.css", "resume"]
    self_contained: true
# uncomment this line to produce HTML and PDF in RStudio:
    knit: pagedown::chrome_print
---
```{r, include=FALSE}
knitr::opts_chunk$set(
  results='asis', 
  echo = FALSE
)
library(tidyverse)
library(ragg)
```
Aside
================================================================================
<center>
![Mark Druffel](`r paste0(here::here(), "/images/my_photo_tight.jpeg")`){style='width:52%;border-radius: 50%;padding-bottom:8px;'}
<br>
<a href='https://www.mark-druffel.com/' target='_blank'><i class="fa fa-home"></i></a>
<a href='mailto:mark.druffel@gmail.com' target='_blank'><i class="fa fa-envelope"></i></a>
<a href='https://github.com/mark-druffel' target='_blank'><i class="fa fa-github"></i></a>
<a href='https://www.linkedin.com/in/markdruffel/' target='_blank'><i class="fa fa-linkedin"></i></a>
</center>

<i class="fa fa-graduation-cap" style='padding-right:6px;'></i> Education {#education}
--------------------------------------------------------------------------------
#### University of Notre Dame
M.S in Business Analytics  

#### Ohio University 
Bachelors in Business Admin

<i class="fa fa-terminal" style='padding-right:6px;'></i> Languages {#languages}
--------------------------------------------------------------------------------
```{r, out.width="90%"}
skills_bar <- function(){
  tibble(
    order = c(1, 2, 3, 4 ,5 , 6, 7),
    language = c("R", "Python", "SQL", "Cypher", "JavaScript", "HTML/CSS", "Bash"),
    skill = c(5, 3, 4.5, 2, 2.5, 3, 2.5)
  ) |>
    mutate(max = 5) |>
    ggplot(aes(x = max, y = reorder(language, -order), width = .6)) +
    geom_col(fill = "grey85") +
    geom_col(aes(x = skill), fill = "grey15") +
    theme_void() +
    labs(y = "Language") +
    theme(
      axis.text.y = element_text(size = 28, family = "Roboto Slab", face = "bold", color = "black", hjust = 1),
      plot.background = element_rect(fill = "#F5FEFD", color = "#F5FEFD"),
      panel.background = element_rect(fill = "#F5FEFD", color = "#F5FEFD")
    )
}
skills_bar()
```

<i class="fa fa-wrench" style='padding-right:6px;'></i> Tools {#tools}
--------------------------------------------------------------------------------
#### Database / Big Data
Snowflake, Aurora, MySQL, MS SQL, Apache Spark, pyspark, sparklyr, Apache Arrow, neo4j, dbplyr, data.table

#### Data Visualization / Dashboard  
ggplot2, shiny, observable, d3.js, Plotly, Highcharts, Apache Superset, Tableau, PowerBI

#### Modeling
tidymodels, caret, keras, tidytext, Apache OpenNLP

#### Devops  
Git, AWS, Digital Ocean, Docker, Apache Airflow, Netlify

#### Design
InVision, Figma, Gimp, Scribis


<i class="fa fa-sitemap" style='padding-right:6px;'></i> Volunteer {#organizations}
--------------------------------------------------------------------------------
#### Civic Software Fdn, Exec Producer  
Delivered a web app that provided longitudinal analysis to the Oregon Department of Education.

Main
================================================================================

Mark Druffel <span class="my-location"><i class="fa fa-map-marker-alt" style='padding-right:4px;'></i>Portland, OR</span> {#title}    
--------------------------------------------------------------------------------
<span class="my-blurb">Data science generalist with a decade of experience working at all levels of organizations. I love using data visualization to understand and communicate insights, ggplot2 is my happy place.</span>

Experience {data-icon=suitcase}
--------------------------------------------------------------------------------

### Senior Data Analyst

DocStation

Remote

2021

First analyst at a start-up where we’re building a platform that enables pharmacists to provide value-based care.  

* Grow capabilities by developing new data models with pyspark, which are managed with an Apache Airflow pipeline. 
* Support operations by developing dashboards with Apache Superset, R Shiny, AWS Aurora, and Snowflake. 
* Perform ad hoc analysis and predictive modeling which has led to improvements in task targeting, sales, and customer retention. 
* Collaborate with engineers to design a scalable analytics architecture. 
* Write pitches for new features and tools based on product analysis. 
* Developed an internal blog for low cost, high-fidelity analysis publishing. 

### Data & Analytics Consultant

Propeller

Portland, OR

2017


Developed and executed data strategies and analytics projects for clients.

* Created a feedback loop between a product team and their end-users by developing a text analysis and NLP pipeline, which automatically identified user pain points from the website and app feedback tools. 
* Designed a prototype app that enabled an HR team to transition to a data-driven recruitment process to improve velocity and candidate quality. 
* Developed and facilitated an analytics workshop that helped a client's business partners understand the analytics process to improve collaboration. 
* Developed internal infrastructure to streamline Propeller's operations including API wrappers, a data pipeline, and automated reporting.

### Business Intelligence Manager

Northern Trust, Hedge Fund Services

Chicago, IL

2013

Managed a global team of reporting and operations analysts.  

* Trained new analysts by teaching SQL, Tableau, R, Python, and others to improve the teams' capabilities and support members' career goals.
* Designed and implemented an analytics pipeline that identified processing bottlenecks and bad code, forecasted demand, etc. enabling the product team to manage tech debt.
* Developed dashboards and reporting using Tableau and eGlue (homegrown).
* Managed access management, data transfer, and data quality assurance.
        
### Senior Consultant

Plante Moran

Chicago, IL

2011

Managed IT audits and risk assessments for clients in various industries.  

### Staff Auditor 

Fifth Third Bank

Cincinnati, OH

2010

Executed financial audits, IT audits, and risk assessments.   


<footer> 
<p class="footer">Resume made with `r fontawesome::fa("r-project", fill = "steelblue")` & [pagedown](https://github.com/rstudio/pagedown), code available on `r fontawesome::fa("github", fill = "black")` [GitHub](https://github.com/mark-druffel/resume)<br/>[mark.druffel@gmail.com](mailto:mark.druffel@gmail.com)
<p/>
</footer>
