---
title: "Mark Druffel"
author: Mark Druffel
date: "`r Sys.Date()`"
output:
  pagedown::html_resume:
    #resume is the default from pagedown, keep it there or have to build all css structures
    css: ["resume.css", "resume"]
    self_contained: true
# uncomment this line to produce HTML and PDF in RStudio:
    knit: pagedown::chrome_print
---
```{r, include=FALSE}
knitr::opts_chunk$set(
  results='asis', 
  echo = FALSE
)
library(tidyverse)
library(ragg)
```
Aside
================================================================================
<center>
![Mark Druffel](`r paste0(here::here(), "/images/my_photo_tight.jpeg")`){style='width:52%;border-radius: 50%;padding-bottom:8px;'}
<br>
<a href='https://www.mark-druffel.com/' target='_blank'><i class="fa fa-home"></i></a>
<a href='mailto:mark.druffel@gmail.com' target='_blank'><i class="fa fa-envelope"></i></a>
<a href='https://github.com/mark-druffel' target='_blank'><i class="fa fa-github"></i></a>
<a href='https://www.linkedin.com/in/markdruffel/' target='_blank'><i class="fa fa-linkedin"></i></a>
</center>

<i class="fa fa-graduation-cap" style='padding-right:6px;'></i> Education {#education}
--------------------------------------------------------------------------------
#### University of Notre Dame
M.S in Business Analytics  

#### Ohio University 
Bachelors in Business Admin

<i class="fa fa-terminal" style='padding-right:6px;'></i> Languages {#languages}
--------------------------------------------------------------------------------
```{r, out.width="90%"}
skills_bar <- function(){
  tibble(
    order = c(1, 2, 3, 4 ,5 , 6, 7),
    language = c("R", "Python", "SQL", "Cypher", "JavaScript", "HTML/CSS", "Bash"),
    skill = c(5, 3, 4.5, 2, 2.5, 3, 2.5)
  ) |>
    mutate(max = 5) |>
    ggplot(aes(x = max, y = reorder(language, -order), width = .6)) +
    geom_col(fill = "grey85") +
    geom_col(aes(x = skill), fill = "grey15") +
    theme_void() +
    labs(y = "Language") +
    theme(
      axis.text.y = element_text(size = 28, family = "Roboto Slab", face = "bold", color = "black", hjust = 1),
      plot.background = element_rect(fill = "#F5FEFD", color = "#F5FEFD"),
      panel.background = element_rect(fill = "#F5FEFD", color = "#F5FEFD")
    )
}
skills_bar()
```

<i class="fa fa-wrench" style='padding-right:6px;'></i> Tools {#tools}
--------------------------------------------------------------------------------
#### Database / Big Data
SQL, Apache Spark, Apache Arrow, neo4j, dbplyr, data.table

#### Data Visualization / Dashboard  
shiny, ggplot2, d3.js, Plotly, Highcharts, Apache Superset, Tableau, PowerBI

#### Modeling
tidymodels, caret, keras

#### Devops  
Git, AWS, Digital Ocean, Docker, Apache Airflow

#### Design
InVision, Figma, Gimp, Scribis


<i class="fa fa-sitemap" style='padding-right:6px;'></i> Volunteer {#organizations}
--------------------------------------------------------------------------------
#### Civic Software Fdn, Exec Producer  
Delivered a web app that provided longitudinal analysis to the Oregon Department of Education.

Main
================================================================================

Mark Druffel <span class="my-location"><i class="fa fa-map-marker-alt" style='padding-right:4px;'></i>Portland, OR</span> {#title}    
--------------------------------------------------------------------------------
<span class="my-blurb">Data science generalist with a decade of experience working at all levels of the organization. I love using exploratory data analysis & data visualization to understand & communicate business problems / solutions - ggplot2 is my happy place. Nowadays, working as the first analyst at a start-up where we're building a platform to enable pharmacists to provide value-based care.</span>

Experience {data-icon=suitcase}
--------------------------------------------------------------------------------

### Senior Data Analyst

DocStation

Remote

2021

Work in all analytics capacities including data-engineering, business intelligence, & data science. Also responsible for respresenting analytics in strategic decisions inlcuding architectural design. 

* Develop data-models in the data-pipeline w/ pyspark & Airflow to expand the data lake, data warehouse, & analytics' capabilities.
* Develop dashboards w/ Superset & Shiny to provide decision support. 
* Perform analysis to identify new business questions or uncover insights that inform strategic decisions.
* Develop models to identify trends and predict outcomes.
* Write pitches for new features & tools based on product analysis.

### Data Scientist  

Propeller

Portland, OR

2017


Helped clients develop data strategies & execute analytics projects, & led Propeller's internal analytics team. A few example projects:  

* Developed text analysis / NLP tools that enabled a health insurance product team to identify / understand user pain points which provided a feedback loop between the team and end-users. 
* Designed a prototype app to enable an HR team to transition to a data-driven recruitment process to improve velocity and candidate quality. 
* Developed & delivered an analytics workshop that helped business teams understand the analytics process to improve collaboration between analytics & business teams. 
* Developed internal infrastructure to streamline Propeller's operations including API wrappers, a data pipeline, & automated reporting.

### Business Intelligence Manager

Northern Trust, Hedge Fund Services

Chicago, IL

2013

Managed a global team of analysts responsible for reporting & ops.  

* Designed & implemented a product analytics process which upended the product strategy & roadmap.
* Developed dashboards & reporting using Tableau & a homegrown tool.
* Developed data-models to expand the data warehouse & analytics' capabilities.
        
### Senior Consultant

Plante Moran

Chicago, IL

2011

Managed IT audits & risk assessments for clients in various industries.  

### Staff Auditor 

Fifth Third Bank

Cincinnati, OH

2010

Executed financial & IT audits, & risk assessments.  